Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-02-18 Thesis/chapter/062-post-emma.tex
finish linreg

%%%%%%%%%%%%%%%%%%%% LIN REG %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{Linear Regression} 
%Initially, it was thought that the resulting layer and thus resistance of a sample is mainly influennced by the Zirconium concentrain in the starting solution $c_{zr}$ and the number of layers applied $\lambda$, but their coefficients are the smallest in absolute values. 
The coefficients of
the Zirconium concentration in the starting solution $c_{zr}$ and the number of layers applied $\lambda$ are largest in value, but the values which are taken by $c_{zr}$ and $\lambda$ are the smallest among the input variables. 
%Initially, it was thought that the resulting layer and thus resistance of a sample is mainly influennced by
%but their coefficients are the smallest in absolute values. 
%
\begin{align}
	\begin{split}
		\label{eq:linreg-phd}
		\hat{\rho} =&  -0.022\cdot c_{zr} -0.022\cdot \lambda -0.0029\cdot v_{DB} + 0.0058\cdot T_{DB} \\
		& -8.5\cdot 10^{-5}\cdot v_{cal} + 0.0026\cdot T_{cal} -0.76
	\end{split}
	\\
	\begin{split}
		\label{eq:linreg-G}
		\hat{\gamma} ={} & 3.2\cdot c_{zr} - 0.97\cdot \lambda - 1.2\cdot v_{DB} + 0.2\cdot T_{DB} \\
			& - 0.014\cdot v_{cal} + 0.13\cdot T_{cal} + 7.2
	\end{split}
\end{align}
%
All terms have the same signs in equations \ref{eq:linreg-phd} and \ref{eq:linreg-G} have the same sign except the intercept and $c_{zr}$. 
$T_{cal}$ and $T_{DB}$ have positive coefficients, i.e. a negative influence on the resistance 
and $\lambda$,$v_{DB}$ and $v_{cal}$ have negative coefficients, i.e. a positive influence on resistance. 
An indication that the data is strongly tainted by error (see also section \ref{sec:res-anova}) is the low $R^2$ score of 0.41 of $\hat\rho$, 
which is (sad but true) even undercut by the $R^2$ of linear fit of $\hat\gamma$, 0.34. 
%The coefficients, though share the signs. 
%This is only true if the extended data set is used and therefore again rather by chance. 
When the linear regression is trained on the complete data set, all terms have the same sign. 
%It is even more astounding that \gls{emma} managed to decrease the average of $\gamma$ an $\rho$ with each generation (see figure \ref{fig:emma-gen}. 
%
\begin{table}[htb]
	\center
	\begin{tabular}{cccccccc}
		        & $c_{zr}$      & $\lambda$     & $v_{DB}$      & $T_{DB}$      & $v_{cal}$     & $T_{cal}$\\
				\hline\hline
				$\rho$          &2.04   &46.58  &1.15   &9.21   &13.50  &27.52\\
				$\gamma$        &10.24  &7.10   &16.46  &10.97  &7.68   &47.55\\
				\hline\hline
	\end{tabular}
	\label{tab:lin-reg-influence}
	\caption{Influences of input variables on output variables in percent according to linear regression.}
\end{table}
%
Thus, even though $T_{cal}$ might have a smaller coefficient in the linear \gls{rf}, the influence on the dependent variable might be larger. 
The influence was calculated by the formula: $I_i=\frac{\bar{x}_i \cdot k_i}{\sum_i \bar{x}_i \cdot k_i}$ with $i=1,\dots,d $ and where $\bar{x}_i$ is average value of the $i$-th input variable and $k_i$ is the coefficient of the $i$-th input variable in the linear regression. 
%The biggest influence on $\rho$ is indeed $T_{cal}$, next with about a third of the influence $T_{DB}$. 
The biggest influence on $\hat\rho$ and $\hat\gamma$ are $\lambda$ and $T_{cal}$. 
While $T_{cal}$ is the second largest influence on $\hat\rho$ as well it is noteworthy that $\lambda$ contributes the least to $\hat\gamma$. 
Furthermore the influence on $\hat\rho$ is dominated by $\lambda$ and $T_{cal}$, while the influences on $\hat\gamma$ are distributed more evenly.
Different distributions were not expected. 
This can have two reasons: 
either the *optimizands* darstellen differen properties and/or signal to noise ratio is too low.
%

$v_{cal}$ and $\lambda$ are well predicted by linear regression as there is a perfect direct proportionality. 
%Do multi linear reg like in Peprah et al. 2017\cite{peprah2017appraisal}.
%

@@

%\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{Grid Search}
For \gls{krr} and {svm} I had to find out what the ideal hyper parameters were. 
So, I anstellen a grid search with the following hyperparameters: 
%kernel=["poly","rbf"]#,"sigmoid"]
%C= np.array(range(1,20))*0.05
%degree=range(1,6)
%epsilon= np.array(range(1,20))*0.2
%gamma=[0.0,0.1,1.0,10.0]
%#param = {"kernel":kernel, "C":C, "degree":degree, "epsilon":epsilon, "gamma":gamma }
%C=[1,0.1]; degree=[3]; epsilon=[1,2]; gamma=['scale']
Now what are C,epsilon and gamma?

>>>>

%%%%%%%%%%%%%%%%%%%% LIN REG %% lin reg %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{Linear Regression} 
%Initially, it was thought that the resulting layer and thus resistance of a sample is mainly influennced by the Zirconium concentrain in the starting solution $c_{zr}$ and the number of layers applied $\lambda$, but their coefficients are the smallest in absolute values.

%\todo{what was fitted how?}
The data obtained from the \gls{emma} optimisation was used to fit a linear model. 
The biggest difference of the linear model to \gls{emma} is that all variables are included, that the \gls{bf}s are strictly linear and that there are no interaction terms. 
The coefficients of the $\lambda$ term have the same sign in equations \ref{eq:emma-phd3},\ref{eq:emma-G3},\ref{eq:emma-phd4},\ref{eq:emma-G4} (\gls{emma} \gls{rf}s) and \ref{eq:linreg-phd},\ref{eq:linreg-G} and have comparable magnitudes too. 
%
%Initially, it was thought that the resulting layer and thus resistance of a sample is mainly influenced by
%but their coefficients are the smallest in absolute values. 
%
\begin{align}
	\begin{split}
		\label{eq:linreg-phd}
		\hat{\rho} &=  -0.022\cdot c_{zr} -0.022\cdot \lambda -0.0029\cdot v_{DB} + 0.0058\cdot T_{DB} \\
		& -8.5\cdot 10^{-5}\cdot v_{cal} + 0.0026\cdot T_{cal} -0.76
	\end{split}
	\\
	\begin{split}
		\label{eq:linreg-G}
		\hat{\gamma} &={}  \qquad 3.2\cdot c_{zr} \,\, - 0.97\cdot \lambda \,\,\quad - 1.2\cdot v_{DB} + \,\,\,\quad 0.2\cdot T_{DB} \\
			& \qquad - 0.014\cdot v_{cal} \quad + 0.13\cdot T_{cal} + 7.2
%		\hat{\gamma} ={} & 3.2\cdot c_{zr} - 0.97\cdot \lambda - 1.2\cdot v_{DB} + 0.2\cdot T_{DB} \\
%			& - 0.014\cdot v_{cal} + 0.13\cdot T_{cal} + 7.2
	\end{split}
\end{align}
%
All terms in equations \ref{eq:linreg-phd} and \ref{eq:linreg-G} have the same sign except the intercept and $c_{zr}$. 
%
More particularly, $T_{cal}$ and $T_{DB}$ have positive coefficients, i.e. a negative influence on the resistance 
and $\lambda$, $v_{DB}$ and $v_{cal}$ have negative coefficients, i.e. a positive influence on resistance. 
An indication that the data is strongly tainted by noise (see also section \ref{sec:res-anova}) is the low $R^2$ score of 0.41 of $\hat\rho$, 
which is (sad but true) even undercut by the $R^2$ of linear fit of $\hat\gamma$, 0.34. 
%The coefficients, though share the signs. 
%This is only true if the extended data set is used and therefore again rather by chance. 
When the linear regression is trained on the complete data set, all terms have the same sign compared to the \gls{emma} data set trained linear model. 
%It is even more astounding that \gls{emma} managed to decrease the average of $\gamma$ an $\rho$ with each generation (see figure \ref{fig:emma-gen}.
$v_{cal}$ and $\lambda$ are well predicted by linear regression as there is a perfect direct proportionality and thus are not displayed here. 
%
\begin{table}[htb]
	\center
	\begin{tabular}{cccccccc}
		        & $c_{zr}$      & $\lambda$     & $v_{DB}$      & $T_{DB}$      & $v_{cal}$     & $T_{cal}$\\
				\hline\hline
				$\hat\rho$          &2.04   &46.58  &1.15   &9.21   &13.50  &27.52\\
				$\hat\gamma$        &10.24  &7.10   &16.46  &10.97  &7.68   &47.55\\
				\hline\hline
	\end{tabular}
	\label{tab:lin-reg-influence}
	\caption{Influences of input variables on output variables in percent according to linear regression.}
\end{table}

%
Regarding the coefficients of the linear model, the zirconium concentration in the starting solution $c_{zr}$ and the number of layers applied $\lambda$ are largest in value, but the values which are taken by $c_{zr}$ and $\lambda$ itself are the smallest among the input variables. 
Thus, even though $T_{cal}$ might have a smaller coefficient in the linear \gls{rf}, the influence on the dependent variable might be larger. 
In order to compare, the influence was calculated by the formula: $I(x_i)=\frac{\bar{x}_i \cdot k_i}{\sum_i \bar{x}_i \cdot k_i}$ with $i=1,\dots,d $ and where $\bar{x}_i= \frac{(x_{min}+x_{max})}{2}$ is average possible value of the $i$-th input variable and $k_i$ is the coefficient of the $i$-th input variable in the linear regression. 
%The biggest influence on $\rho$ is indeed $T_{cal}$, next with about a third of the influence $T_{DB}$. 
The biggest influence on $\hat\rho$ is  $\lambda$, followed by $T_{cal}$. 
While $T_{cal}$ is the second largest influence on $\hat\rho$ as well it is noteworthy that $\lambda$ contributes the least to $\hat\gamma$. 
That means that according to the linear regression, the number of layers increases the overall resistance of the zirconium ceramics while a lower calcination temperature leads to less defects. 
Interestingly, the number of layers has the least amount of influence on the number probability of defects, which seems to be an artefact of the noise rather than a process property. 
%Furthermore the influence on $\hat\rho$ is dominated by $\lambda$ and $T_{cal}$, while the influences on $\hat\gamma$ are distributed more evenly.
%Different distributions were not expected. 
The two very different distributions of influence among the input variables can have three reasons:
%This can have two reasons: 
(1) the linear function is not a suitable regression function for the data distribution.
(2) the signal to noise ratio is so low that the noise rather than the signal was fitted.
(3) the \textit{optimizands} indeed represent different properties of the material.
%either the *optimizands* darstellen differen properties and/or signal to noise ratio is too low.
%

%Do multi linear reg like in Peprah et al. 2017\cite{peprah2017appraisal}.
%

@@

%\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{Grid Search}
The ideal hyper parameters have to be found for \gls{krr} and \gls{svm}.
To do so a grid search over a set of hyper parameters was executed. 
Both \gls{krr} and \gls{svm} following kernel: radial basis function, sigmoid, and polynomial with degree 1 to 4. 
Gamma = {

%KRR
%gamma=[0.01, 0.05, 0.1, 0.5, 1.0, 5, 10] #HPGS
%alpha=[0.01, 0.02, 0.05, 0.1, 0.2, 0.5, 1, 2] #, 10, 50, 100] #HPGS

%SVM
%C= np.array(range(1,20))*0.05 # HPGS
%epsilon= np.array(range(1,20))*0.2 # HPGS
%gamma=[0.01, 0.05, 0.1, 0.5, 1.0, 5, 10, "scale"] # HPGS

%kernel=["poly","rbf"]#,"sigmoid"]
%C= np.array(range(1,20))*0.05
%degree=range(1,6)
%epsilon= np.array(range(1,20))*0.2
%gamma=[0.0,0.1,1.0,10.0]
%#param = {"kernel":kernel, "C":C, "degree":degree, "epsilon":epsilon, "gamma":gamma }
%C=[1,0.1]; degree=[3]; epsilon=[1,2]; gamma=['scale']
Now what are C,epsilon and gamma?
